---
title: Waihāhā hut and Kakaho Campsite
---

- **Location**: Pureora forest
- **Date**: from 2023/09/02 to 2023/09/04

Three of us finally managed to squeeze two nights out for an end-of-winter camping trip.
We headed to the [Pureora Forest Park](https://www.doc.govt.nz/parks-and-recreation/places-to-go/waikato/places/pureora-forest-park/?tab-id=50578) to walk the [Waihāhā hut Track](https://www.doc.govt.nz/parks-and-recreation/places-to-go/waikato/places/pureora-forest-park/things-to-do/waihaha-track/). The track follows the Waihāhā River and it offers a nice and easy walk across a variety of vegetation. 

```{r}
#| echo: false

library(leaflet)

leaflet() %>% 
    addTiles() %>% 
    setView(lat =-38.698258, lng = 175.627927, zoom = 13) %>% 
    addMarkers(lat=-38.695475, lng=175.600927, label = "Waihāhā hut", labelOptions = labelOptions(noHide = T, direction = "bottom")) %>% 
    addMarkers(lat=-38.699846, lng=175.681653, label = "Starting point", labelOptions = labelOptions(noHide = T, direction = "bottom")) %>% 
    addProviderTiles(provider = providers$OpenTopoMap) %>% 
    addProviderTiles(provider = providers$Stamen.Terrain)
```


We spent the night at the Waihāhā hut, and the next day, we made our way back to the car. We decided to take the day slow, visiting Kinloch and then relaxing at the Wairakei Terraces. 

Given that the weather was nice and would have remained clear until the next afternoon, we decided to camp out for another night. We headed to the [Kakaho Campsite](https://www.doc.govt.nz/parks-and-recreation/places-to-go/waikato/places/pureora-forest-park/things-to-do/kakaho-campsite/). The site was desert, we were the only one there. The night was clear, and we got treated to an amazing starry sky while trying to keep warm next to a campfire.

```{r}
#| echo: false

leaflet() %>% 
    addTiles() %>% 
    setView(lat=-38.564407, lng=175.718658, zoom = 13) %>% 
    addMarkers(lat=-38.564407, lng=175.718658, label = "Waihāhā hut", labelOptions = labelOptions(noHide = T, direction = "bottom")) %>% 
    addProviderTiles(provider = providers$OpenTopoMap) %>% 
    addProviderTiles(provider = providers$Stamen.Terrain)
```

After a quite cold night, we packed up and completed the short [Rimu Track Loop](https://www.doc.govt.nz/parks-and-recreation/places-to-go/waikato/places/pureora-forest-park/things-to-do/rimu-walk/) within the Pureora Forest. 

## Notes for the future

- For winterish camping, source an Italian Army Blanket (or similar) or bring a hot water bottle. The night was fine, but it would have been nicer to have an extra source of warmth.
- Instant polenta is a great camping food. It packs compact and it's filling. It might be better than pasta. 
- Need to learn some handy knots


