---
title: "Students Review"
---

When I started my PhD, I have also begun tutoring every semester. I enjoy teaching, interacting with students and sharing the knowledge I am passionate about. I often think about how to be a better educator, how to set up my tutorials and how to create a positive environment in my classes. I like to look at teaching through the lens of my past as a magician. Teaching is an act with a story to convey, attention to grab, and audience participation should be encouraged.

My idea of teaching may be far away from what the students want and need, I know. Unfortunately, the courses I teach do not ask students to provide feedback on their tutors, and I find this absurd. We are an integral part of their education experience, we should be able to know how we are doing and what we should work on. So, I have been actively collecting students' evaluations for all the courses I teach. I do this at the end of each semester through an anonymous survey that students can voluntarily fill out.

In the name of transparency, I have decided to post all the anonymous feedback here. I will update this page each semester, and I will address the comments and reflect on what I need to work on.

As a side note, I try to encourage students to provide constructive feedback, and I try to stress that negative feedback is more than welcome. I really want to improve and work on how to be better, and negative feedback, if constructive, helps highlight things to change and work on. As such, I won't hide any comments except if they are un-constructively negative or contain some sensitive information. I will add a note if this happens.

```{r}
#| echo: false
#| output: false
#| warning: false
#| message: false

library(tidyverse)
library(janitor)
library(here)
library(wordcloud2)
library(kableExtra)
library(waffle)

# Load data and set it up appropriately
raw_feedback <- read_csv(here('educating','data', 'feedback_collected.csv'))
questions    <- colnames(raw_feedback)

raw_feedback <- raw_feedback %>% 
    pivot_longer(cols = everything(),
                 names_to = 'question',
                 values_to = 'answers')
```

```{r}
#| echo: false
#| message: false
#| warning: false
descriptors <- raw_feedback %>% 
    filter(question %in% questions[5:9]) %>% 
    mutate(answers = tolower(answers)) %>% 
    drop_na() %>% 
    group_by(answers) %>% 
    summarise(freq = n()) %>% 
    rename(word = answers)

wordcloud2(descriptors, minRotation = -pi/2, maxRotation = -pi/2, backgroundColor = '#f8f4ea')
```

*One of the survey's question is to provide 3 words that describe me as a tutor. Above is a summary of the words provided so far*

## Students' marks

Let's start with a simple and fun (hopefully) section where I swap the roles with the students and they are able to grade my work.

```{r}
#| echo: false
#| message: false
#| warning: false

marks_plot <- raw_feedback %>% 
    filter(question == questions[1]) %>% 
    replace_na(list(answers= "Unanswered")) %>% 
    count(answers) %>% 
    ggplot(aes(fill = answers, values = n)) +
    geom_waffle(n_rows = 5,
                size   = 1, 
                color  = "#f8f4ea",  
                flip   = F,
                make_proportional = TRUE,
                use_glyph = "graduation-cap") +
    scale_fill_manual(values = c("#008080", "purple" , "gray")) +
    labs(fill = "") +
    coord_equal() +
    theme_void() +
    theme(
          panel.background = element_rect(fill="#f8f4ea", color=NA),
          plot.background  = element_rect(fill="#f8f4ea", color=NA),
          legend.position = "bottom"
          )
```

```{r, dev = "png", dev.args=list(bg="transparent")}
#| echo: false
#| message: false
#| warning: false
marks_plot
```
Each square represents 1% of the overall scores received by students. I'm glad to see that the vast majority considered my tutorial "Above average" and there are no *Below average*.

In terms of marks, the grades below are scaled by their relative proportion. The larger the letter, the higher the number of students that selected that grade. Again, I'm happy to see the *A+* and *A* being large!

```{r}
#| echo: false
#| message: false
#| warning: false

marks_2 <- raw_feedback %>% 
    filter(question == questions[2]) %>% 
    mutate(total_answers = n(),
           answers = factor(answers, levels = c('A+', 'A', 'A-', 'B+', 'B','B-'))) %>% 
    group_by(answers, total_answers) %>% 
    summarise(count = n()) %>% 
    mutate(x_value = case_when(answers == 'A+' ~ 0,
                               answers == 'A'  ~ 5,
                               answers == 'A-' ~ 10,
                               answers == 'B+' ~ 15,
                               answers == 'B'  ~ 20),
           y_value = 0,
           proportion = (count / total_answers)*100)

grade_plot <- marks_2 %>% 
    ggplot(aes(x=x_value, y=y_value)) +
    geom_text(aes(label=answers, size = proportion), 
              colour = '#fe9f2e', 
              show.legend = F) +
    scale_size(range = c(8, 24), guide = F) +
    coord_cartesian(xlim = c(-1, 21)) +
    theme_minimal() +
    theme(axis.text.y = element_blank(),
          axis.text.x = element_blank(),
          axis.title  = element_blank(),
          panel.grid  = element_blank(),
          panel.background = element_rect(fill='transparent', color=NA),
          plot.background  = element_rect(fill='transparent', color=NA))
```

```{r, dev = "png", dev.args=list(bg="transparent")}
#| echo: false
#| message: false
#| warning: false
grade_plot
```

## What students appreciate

Now, we get to the core of the feedback. I will highlight at the top the comments that I think represent the major ideas. Nonetheless, at the end of the section, you can find an exhaustive table with all the feedback.

> You were always super nice and friendly and you always made me feel super comfortable coming to class. I was also never nervous to ask you questions about assignments cause you were always very informative and good with helping.

> You did a great job in tutorials giving people opportunities to ask for help of they needed it and checking to make sure we were on the right track. Also you kept it engaging by relating the various topics and ideas to your own interest and the wider ideas around the topic, encouraging broader thinking about it.

> Tutorials are fun and friendly environments.

There are three main elements I think students appreciate:

1- The content should be presented differently from the lecturers. This makes the tutorial feel less like a simple repetition and more like an opportunity to learn more and/or understand better.

2- Give people time to ask questions. We all vary with how comfortable we are in asking questions in class. I encourage discussions, debates and questions since the very first tutorial to create an environment where everyone feels comfortable being an active part.

3- Engage. We all agree that listening to one person talking for two hours is boring. So why do this? Showing a more fun and natural side helps create a connection, keep the attention high and make the tutorial time more enjoyable.

> I felt like the tutorials were quite good, maybe trying to put more organisation with our meetings and not just us asking questions and more information being given would be good.

I agree on this point. One of the aspects I need to work more on is structure (more on this in the next session). I do not want to have everything predefined, as this is counterproductive, but I will try to define at the beginning of the tutorial the key areas I will discuss.

```{r}
#| echo: false
#| warning: false
#| message: false 
appreciation <- raw_feedback %>% 
    filter(question == questions[3]) %>% 
    select(answers) %>% 
    rename(Feedback = answers) %>% 
    drop_na()

kbl(appreciation) %>% 
    kable_material(c("hover")) %>% 
    scroll_box(width = "100%", height = "400px")
    
```

## What students think I should do better

> Sometimes the discussion time in tutorials felt too long and often we'd finish the task and end up going off task. Maybe less small group discussion and then a longer period for class discussion would have been more to my personal preference, but its not a major issue cause there was normally plenty of time anyway. Occasionally you start to rush when you get excited, which is fun to see but it can lead to us missing certain points sometimes.

I will try next year to have more class discussions and less small group work. A couple more people pointed this out. I believe that small groups would have encouraged people to talk more by reducing the pressure of having to speak out loud in front of everyone. However, doing this takes time that could be used differently.

> Found the we had to rush some tutorials to fit within the 2hr time. Could try changing what info to include / exclude to fit within the 2hrs and no information is rushed. Could spend a little time going over lectures etc.

This is a fair point. I almost always take the full 2 hours, most likely because I like to digress. As pointed out above, next year I will try to structure each tutorial a bit more. Specifically, I will highlight at the beginning the major point we will discuss, and I will add a recap at the end. However, I will keep some improvisation. I believe that having just a general structure of what to talk about allows for the exploration of topics, concepts and ideas that otherwise won't be addressed. Tutorials, in my view, are not just a recap of the lectures but a moment where we can dive deeper into a topic or create connections across different areas. They are useful to broaden our understanding of the concepts discussed in the lectures and, by doing so, learn the material better.

> Would appreciate more concise marking, and felt marking scores were abit harsh sometimes compared to other students or the feedback received.

Given the multiple comments appreciating the lengthy feedback on the essays, I will not plan to change this. Assignments and exams are not just a test but an opportunity to improve and gain skills. By providing detailed feedback, students are able to improve their future work. I agree that I can be strict with my marking. This is partly caused by my study background and the way I have been assessed. Partly because I try to mark focusing hardly on the reasoning. That is, I don't see just repeating the content from a book or lectures as being enough for an A+. The reasoning behind an answer is important. Nonetheless, in the class I teach, us tutors try to match our criteria, so if I am being too harsh, other tutors and professors will call me out on this before the marks are finalized.

```{r}
#| echo: false
#| warning: false
#| message: false 
improve <- raw_feedback %>% 
    filter(question == questions[4]) %>% 
    select(answers) %>% 
    drop_na()
kbl(improve) %>% 
    kable_material(c("hover")) %>% 
    scroll_box(width = "100%", height = "400px")
```

## Extra comments

As my survey is meant to be quick, I leave the opportunity to express other ideas freely.

```{r}
#| echo: false
#| warning: false
#| message: false 
extra <- raw_feedback %>% 
    filter(question == questions[10]) %>% 
    select(answers) %>% 
    drop_na()

kbl(extra) %>% 
    kable_material(c("hover")) %>% 
    scroll_box(width = "100%", height = "400px")
```
