---
title: "Students Review"
format: 
  html:
    page-layout: full
---

***UPDATED AT THE END OF 2024***

I love teaching. I love spending time in class discussing interesting
topics and having conversations with students. It's one of my favourite
parts of being a young researcher. I often think about how to be a
better educator, set up my tutorials, and create a positive environment
in my classes. How can I grab and maintain students' attention
(especially at 8.00 am on a Monday)? How can I explore a concept from a
different perspective from the one provided in class by professors? How
can I create and encourage a class environment without a strict
hierarchical structure?

I'm by no means close to implementing my ideal lab time. A time focused
on active learning based on challenging but meaningful activities that
expand what was covered in class. A time when we, the educators, guide
conversations and discussions rather than simply providing information.
Part of the cause is definitely my fault for not being able to fully
implement and create what I wish my labs would be. The other part is
played by the university system not considering laboratories and
tutorials that important, which is evident in underfunding for tutors,
stagnant teaching material and the lack of feedback we receive.

Because of this, I have been proactively collecting reviews and feedback
from the students in my tutorials. At the end of each semester, I
encourage them to constructively review my work as an educator. I do so
through an anonymous survey, which I keep short and light, knowing that
no one wants to spend much time answering questions, especially when the
exam period is approaching. In class, I encourage students to provide
any type of feedback, positive or negative, especially negative, as I
want to use it as a building block to improve semester through semester.

We all know that often feedback is not really used to change anything.
Most of the time, it is just assessed by the administration to see if
some KPIs have been met. I hate that. So, in the name of transparency
and self-accountability, I decided to post all the anonymous feedback
here (this is clearly stated in the survey). In the page below, I try to
summarise the overall reviews, and I address the points I believe are
important for me to consider or reply to.

*Disclaimer: I won't censor any comments except those containing private
or sensitive information irrelevant to my role as an educator. I will
add a note if this happens.*

```{r}
#| echo: false
#| output: false
#| warning: false
#| message: false

library(tidyverse)
library(janitor)
library(here)
library(wordcloud2)
library(kableExtra)
library(waffle)
library(glue)

# Load data and set it up appropriately
raw_feedback <- read_csv(here('educating','data', 'feedback_collected.csv'))
questions    <- colnames(raw_feedback)

raw_feedback <- raw_feedback %>% 
    pivot_longer(cols = everything(),
                 names_to = 'question',
                 values_to = 'answers')
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-cap: "Describe me as a tutor in three words. A summary of the responses collected so far"

descriptors <- raw_feedback %>% 
    filter(question %in% questions[5:9]) %>% 
    mutate(answers = tolower(answers)) %>% 
    drop_na() %>% 
    group_by(answers) %>% 
    summarise(freq = n()) %>% 
    rename(word = answers)

wordcloud2(descriptors, minRotation = -pi/2, maxRotation = -pi/2, backgroundColor = '#f8f4ea')
```

## Students' marks

I like to give students the opportunity to "sit on the other side of the
desk" and have the opportunity to review my work with a grade. The first
question is a benchmark to see how I am doing compared to the other
classes they take. I have not completed my undergrad in New Zealand, so
I do not have a clear idea of what a good or bad tutorial can be.

```{r}
#| echo: false
#| message: false
#| warning: false

# Compute percentages
question_1_percentages <- raw_feedback %>% 
    filter(question == questions[1]) %>% 
    replace_na(list(answers="Unanswered")) %>% 
    table() %>% 
    prop.table()

marks_plot <- raw_feedback %>% 
    filter(question == questions[1]) %>% 
    replace_na(list(answers= "Unanswered")) %>% 
    count(answers) %>% 
    ggplot(aes(fill = answers, values = n)) +
    geom_waffle(n_rows = 10,
                size   = 1, 
                color  = "#f8f4ea",  
                flip   = T,
                make_proportional = TRUE,
                use_glyph = "graduation-cap") +
    scale_fill_manual(values = c("#008080", "purple" , "gray"),
                      labels = c(glue("Above Average\n({round(question_1_percentages[1]*100)}%)"),
                                 glue("Average\n({round(question_1_percentages[2]*100)}%)"),
                                 glue("Not Responded\n({round(question_1_percentages[3]*100)}%)"))
                      ) +
    labs(fill = "",
         title = "How would your rate my tutorials\n compared to other tutorials/classes?") +
    coord_equal() +
    theme_void() +
    theme(
          panel.background = element_rect(fill="#f8f4ea", color=NA),
          plot.background  = element_rect(fill="#f8f4ea", color=NA),
          legend.position = "bottom",
          legend.margin = margin(0,0,5,0),
          plot.title = element_text(hjust = .5)
          )
```

```{r, dev = "png", dev.args=list(bg="transparent")}
#| echo: false
#| message: false
#| warning: false
marks_plot
```

80% of those who completed the survey considered my tutorials above
average according to their experience. About one-sixth retained them to
be within the average range, and no one was below average. I believe
this is a great benchmark that shows that my classes are (1) positively
different or at least similar to other classes and (2) appreciated by
students.

------------------------------------------------------------------------

The second question asks literally for a grade. I think it could be a
cathartic moment being able to grade the person who has been grading
your coursework. Moreover, if taken seriously, grading can make you
reflect on the way you evaluate experiences. Was something really that
good or that bad? Were the tutorials really so dull or so exciting?
Maybe I was just tired or maybe I just liked the content but not the
delivery.

```{r}
#| echo: false
#| message: false
#| warning: false

question_2_percentages <- raw_feedback %>% 
    filter(question == questions[2]) %>% 
    replace_na(list(answers="Unanswered")) %>% 
    table() %>% 
    prop.table() %>% 
    as_tibble()
question_2_percentages$answers <- factor(question_2_percentages$answers, levels = c("A+", "A", "A-", "B+", "B", "B-", "Unanswered"))

grade_plot <- question_2_percentages %>% 
    ggplot(aes(y=question, x=n, fill=answers)) +
    geom_col(position = "fill", width = .15) +
    geom_text(aes(label = paste0(round(n * 100), "%")),
              position = position_fill(vjust = 0.5),
              size = 4) +
    labs(fill  ="",
         title = "What grade do you think I should recieve as a tutor?") +
    scale_fill_brewer(palette="BuGn", direction = -1) +
    guides(fill = guide_legend(nrow = 1, reverse = T)) +
    theme(
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.border = element_blank(),
        panel.grid = element_blank(),
        legend.background = element_rect(fill="transparent", color=NA),
        panel.background = element_rect(fill="#f8f4ea", color=NA),
        plot.background  = element_rect(fill="#f8f4ea", color=NA),
        legend.position = "bottom",
        plot.title = element_text(hjust = .5)
      ) +
    scale_y_discrete(expand = expansion(mult = .1)) +
    scale_x_continuous(labels = scales::percent)

```

```{r, dev = "png", dev.args=list(bg="transparent")}
#| echo: false
#| message: false
#| warning: false
grade_plot
```

The grade aligns with the coarse benchmark above. 87% of students who
completed the survey would be happy to grade my work within the A range
(A-, A, A+), and over half of these grades are an A+. Although we often
dislike skewed distribution, I think this is a good one. There are no
grades below a B, so I think I have happily passed my exam for now.

## What students appreciate

There are a few core trends that started to come up over time. Firstly,
students appreciate being in an environment that supports and encourages
asking questions and sharing thoughts and ideas without worrying. I'm
very glad this is a shared sentiment in my classes as this is one of my
personal goals towards an ideal cooperative, collaborative and welcoming
class.

> I’ve had the pleasure of being in your tutorial stream 2 years in a
> row and have enjoyed it both times. You encourage discussion so
> naturally and are incredibly supportive when students share their
> ideas even if they’re not necessarily the answer you were looking for.
> I really appreciate the depth with which you explain the lab topics
> and truly think my learning has been much improved in the lab
> sessions!

> Support! You were very supportive and accurately explained what was
> required to do well in this class, and explained what we did not need
> to know as extensively - which was much appreciated as often times
> labs can be seen as just an overload of information.

> You did a great job in tutorials giving people opportunities to ask
> for help of they needed it and checking to make sure we were on the
> right track. Also you kept it engaging by relating the various topics
> and ideas to your own interest and the wider ideas around the topic,
> encouraging broader thinking about it.

A second topic seems to be engagement. All those years spent performing
as a magician are paying back now. I've always treated teaching as a
magic act. You need to be able to draw and maintain attention, convey a
story and have fun. I always find interesting how some of the most
popular "academic" videos are of professors doing something unexpected
and interesting. I think we (educators) should all experiment in our
classes with the way we present, the way we interact with students and
the activities we do.

> You explained all the concepts really well, and often in different
> ways if we didn't understand. You also made tutorials fun and worth
> coming to and I always left feeling like I've learnt something. Yours
> is also the only tutorials that I looked forward coming to!

> Really engaging, even though I hated the mini presentations idea
> initially it did help me prepare for a presentation assignment in
> another paper! You are very knowledgeable, helpful and clearly
> passionate about teaching others about the brain!

A specific reply to the last comment. I totally understand how
mini-presentations might not be a hit for many people. Public speaking
sucks, especially when you don't have much time to prepare. However, as
I said in most of my tutorials, the only way to improve in public
speaking is... by publicly speaking. There is no real way around that.
To be honest, presentations are not necessarily my own idea, but I hope
that by creating a welcoming environment, I'm making them less
stressful. The way I see it is that tutorials are the perfect
opportunity to practice presenting, as we are among people we know and
there is no judgment involved. I'm glad they helped you with another
paper!

Indeed, I've just found another fellow student sharing the same
sentiment. I'll keep this in mind for next year; maybe I'll try to sneak
some tips and techniques during the tutorials.

> Integrating mini presentations which helps us build our public
> speaking and be more confident with our knowledge

```{r}
#| echo: false
#| warning: false
#| message: false 
appreciation <- raw_feedback %>% 
    filter(question == questions[3]) %>% 
    select(answers) %>% 
    rename(Feedback = answers) %>% 
    drop_na()

kbl(appreciation) %>% 
    kable_minimal(c("hover")) %>% 
    scroll_box(width = "100%", height = "400px")
    
```

## What students think I should do better

In this section, I will try to reply to some of the comments I believe
are interesting, or that report sentiments shared by different students.

> I thought you were excellent, the only reason I didn’t give you an A+
> is because I felt like you could could go even further by dumbing it
> down and putting course content into other contexts so it would be
> easier to learn/retain

This is a great point. Sometimes I'm scared of providing external
context/examples because my areas of expertise and interests are usually
highly technical and I don't want to scare people off from a topic.
However, next year I'll do my best to provide external context. Maybe I
can get a better sense of everyone's interests and try to also draw from
the knowledge of other students in the class. I like the idea of
students helping other students and me understanding something in more
detail.

> Maybe instead of presenting in front of the class you could do a group
> discussion activity instead.

> Sometimes the discussion time in tutorials felt too long and often
> we'd finish the task and end up going off task. Maybe less small group
> discussion and then a longer period for class discussion would have
> been more to my personal preference, but its not a major issue cause
> there was normally plenty of time anyway.

Indeed, discussions is something I need to work more on. I tend to lean
towards small group discussions because they tend to engage more
students, especially those who are more afraid to talk in front of
everyone. However, the downside is that people do not get to hear
possibly interesting thoughts and ideas that have been shared within
other groups. Next year I will try to (1) add more discussion time and
(2) shortening the small groups discussions and giving more space to a
class discussion. Just one note, as I'm not totally in control of the
lab material and activities, sometimes it's just not possible to add
activities that have not been scheduled by professors. Some professors
are happy to give us more freedom for how we run the labs, but others
are stricter and what they want us to do.

> Rather than having us get up and present, make more interactive
> lessons like the aphantasia ones where we did a little memory test
> Presentations aren't helpful, there should be another more interactive
> way. We don't have enough time to do research or to prepare and
> present and the entire class ends up repeating each other or telling
> false info.

I don't agree that presentations are not useful (see comment in the
section above). However, I agree that tutorials should be more
interactive. This is kind of a tricky point to address. I agree with
you, there should be more interactive ways to run tutorials. Last year,
I pushed towards this direction by crafting the simulated EEG-based liar
detection activity for PSYCH 305. This year, I created and organized the
activity with the portable EEGs. However, I need to strike a balance
between what I would like to do and what the university is happy to
fund. The two activities above required quite a bit of time to be
organized, some of which was out of my free time. In the background, I'm
trying to push for making psych tutorials real laboratories. However, I
am not the one making the final decisions nor the one deciding how many
hours tutors are paid. What I should do, though, is find ways to sneak
in interactivity during standard tutorials. These activities should be
easy to organize and incorporate with professors' requirements. I'll
think of some ideas during the summer!

> Only suggestion I have is to speak slower. Your excitement and English
> are amazing, but when you speak really fast with excitement, it made
> it difficult to understand and keep up sometimes. Occasionally you
> start to rush when you get excited, which is fun to see but it can
> lead to us missing certain points sometimes Honestly, thought you were
> amazing. Maybe you could just slow down sometimes with your
> explanations because it can be a bit hard to keep up with occasionally
> (not often) i couldn’t understand what you were saying when you spoke
> fast Maybe speaking a little bit slower is better Talking a bit slower
> would help a lot for better understanding :)

All these comments are from 2023. I totally agree with you all, I know I
let myself be taken by the excitement of the topics. Plus, Italians
speak fast, so my background does not help. I hope this year I've done a
better job on this. No one pointed this out. If anything, someone
highlighted that I have made changes for the best (below). However, I
have caught myself speeding up, and it is something I need to pay
constant attention to. So I'll leave these comments as a reminder for
the next year.

> Nothing! I think you truly have taken into account feedback from
> previous years (or perhaps I am just used to your teaching style) and
> it’s been great.

```{r}
#| echo: false
#| warning: false
#| message: false 
improve <- raw_feedback %>% 
    filter(question == questions[4]) %>% 
    select(answers) %>% 
    drop_na()
kbl(improve) %>% 
    kable_minimal(c("hover")) %>% 
    scroll_box(width = "100%", height = "500px")
```

## Extra comments

As my survey is meant to be quick, I leave the opportunity to express
other ideas freely.

```{r}
#| echo: false
#| warning: false
#| message: false 
extra <- raw_feedback %>% 
    filter(question == questions[10]) %>% 
    select(answers) %>% 
    drop_na()

kbl(extra) %>% 
    kable_minimal(c("hover")) %>% 
    scroll_box(width = "100%", height = "400px")
```
